A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-10-29 paper/main.tex
Fix URL plus minor stuff

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/slicescolorbars}
    \caption{Results of the mixed-effects group-level (N=14) GLM $t$-contrasts
        for the audio-description of the movie ``Forrest Gump''.
        Significant clusters (Z>3.4, p<0.05 cluster-corrected) are overlaid on
        the MNI152 T1-weighted head template (grey).
        Light grey: The audio-description's field-of-view
        (cf. \citep{hanke2014audiomovie}).}
    \label{fig:results}
\end{figure*}

@@

% (proper) nouns > con
The two contrasts that contrasted nouns and proper nouns respectively to
coordinate junctions yielded increased activation partially located in early
sensory regions (Heschl's Gyrus; \citep{saenz2014tonotopic}) and most
prominently adjacent regions bilaterally (planum temporale; superior temporal
gyrus; \citep{arsenault2015distributed, mesgarani2014phonetic}).
% why these contrasts nous & proper nouns
We chose nouns and proper nouns for these two contrasts because they represent
linguistically similar concepts but are yet uncorrelated in the German language
and stimulus (cf. Figure \ref{fig:reg-corr}).
% coordinate conjunctions
We contrasted nouns and proper nouns respectively to coordinate conjunctions
because nouns and proper nouns are linguistically different to coordinate
conjunctions as well as uncorrelated.
% “interpretation”
Despite the fact that
nouns and proper nouns are uncorrelated, both contrasts lead to largely
spatially congruent clusters. Results suggest that models based on our
annotation of similar linguistic concepts correlate with hemodynamic activity in
spatially similar areas.
% not driven by coordinate conjunction regressors
We confirmed the validity of these interpretation by testing if the spatial
congruency could be attributed to a negative correlation of coordinate
conjunctions with the modeled time series which turned out not to be the case.
% why it's cool
In summary, results of our exploratory analyses suggest that the annotation of
speech meets the quality requirements to be used as the basis for model-based
analyses that investigate language perception under more ecologically valid
conditions.

@@

osf.io: The annotation as both a tab-separated values (TSV) formatted table and
TextGrid file as well as scripts and data of the analysis, doi:
\href{dx.doi.org/10.17605/OSF.IO/GFRME}{10.17605/OSF.IO/GFRME}

>>>>

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/slicescolorbars}
    \caption{Results of the mixed-effects group-level (N=14) GLM $t$-contrasts
        for the audio-description of the movie ``Forrest Gump''.
        Significant clusters (Z>3.4, p<0.05 cluster-corrected) are overlaid on
        the MNI152 T1-weighted head template (grey).
        Light grey: The audio-description dataset's field-of-view
        (cf. \citep{hanke2014audiomovie}).}
    \label{fig:results}
\end{figure*}

@@

% (proper) nouns > con
The two contrasts that contrasted nouns and proper nouns respectively to
coordinate junctions yielded increased activation partially located in early
sensory regions (Heschl's Gyrus; \citep{saenz2014tonotopic}) and most
prominently adjacent regions bilaterally (planum temporale; superior temporal
gyrus; \citep{arsenault2015distributed, mesgarani2014phonetic}).
% why these contrasts nous & proper nouns
We chose nouns and proper nouns for these two contrasts because they represent
linguistically similar concepts but are uncorrelated in the German language
and stimulus (cf. Figure \ref{fig:reg-corr}).
% coordinate conjunctions
We contrasted nouns and proper nouns respectively to coordinate conjunctions
because nouns and proper nouns are linguistically different to coordinate
conjunctions as well as uncorrelated.
% “interpretation”
Despite the fact that
nouns and proper nouns are uncorrelated, both contrasts lead to largely
spatially congruent clusters. Results suggest that models based on our
annotation of similar linguistic concepts correlate with hemodynamic activity in
spatially similar areas.
% not driven by coordinate conjunction regressors
We confirmed the validity of these interpretation by testing if the spatial
congruency could be attributed to a negative correlation of coordinate
conjunctions with the modeled time series which turned out not to be the case.
% why it's cool
In summary, results of our exploratory analyses suggest that the annotation of
speech meets basic quality requirements to be a basis for model-based
analyses that investigate language perception under more ecologically valid
conditions.

@@

osf.io: The annotation as both a tab-separated values (TSV) formatted table and
TextGrid file as well as scripts and data of the analysis, doi:
\href{http://dx.doi.org/10.17605/OSF.IO/GFRME}{10.17605/OSF.IO/GFRME}
